% Pranav Patil's Resume Template
% Enhanced with Jinja2 placeholders for AI-powered customization

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\usepackage{multicol}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1


%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{center}
    {\Huge \scshape Pranav Patil} \\ \vspace{2pt}
    Pune, Maharashtra \\
    \href{tel:+917249562289}{\faPhone\ +91 7249562289} ~
    \href{mailto:pranavpatil7896@gmail.com}{\faEnvelope\ pranavpatil7896@gmail.com} ~
    \href{https://www.linkedin.com/in/pranavpatil6}{\faLinkedin\ linkedin.com/in/pranavpatil6} ~
    \href{https://github.com/losthumanity}{\faGithub\ github.com/losthumanity}
\end{center}
\vspace{-2pt}

%-----------PROFESSIONAL SUMMARY-----------
\section{PROFESSIONAL SUMMARY}
\normalsize{Software Engineer proficient in Python with a strong foundation in AI/ML concepts, applicable to perception systems. Experienced in developing robust, scalable applications and CI/CD pipelines, demonstrating strong software engineering best practices. Possesses expertise in data structures, algorithms, and cloud platforms like AWS.}
\vspace{-8pt}

%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vishwakarma Institute of Technology, Pune}{August 2022 - May 2026}
      {B.Tech - Information Technology - \textbf{CGPA} - \textbf{8.62}}{Pune, Maharashtra}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{PROJECTS}
    \vspace{-5pt}
    \resumeSubHeadingListStart

     \resumeProjectHeading
          {\href{https://github.com/losthumanity/video-source-verification}{\textbf{\large{\underline{Video Source Identification and Verification}}} \faExternalLink} $|$ \large{\underline{Python, Pytorch, CNN, ResNet50}}}{}\\
          \resumeItemListStart

            \resumeItem{\normalsize{Collaborated in a 5-engineer team, employing software engineering best practices like backlog management and user stories to develop an end-to-end perception prototype.}}

            \resumeItem{\normalsize{Performed comprehensive comparative analysis of deep learning CNN models (e.g., ResNet50) on precision-latency trade-offs, critical for real-time perception systems.}}

            \resumeItem{\normalsize{Achieved top 5\% performance on an IEEE benchmark with 95\% precision in content detection, demonstrating robust computer vision and machine learning algorithms.}}

          \resumeItemListEnd
          \vspace{-13pt}

     \resumeProjectHeading
          {\href{https://github.com/losthumanity/medical-doc-ai}{\textbf{\large{\underline{AI-Powered Medical Document Analysis Platform}}} \faExternalLink} $|$ \large{\underline{Python, LangChain, Fast-API}}}{}\\
          \resumeItemListStart

            \resumeItem{\normalsize{Engineered an end-to-end Python RAG pipeline for processing complex data from 1000+ documents, enabling natural language querying for advanced information retrieval.}}

            \resumeItem{\normalsize{Applied machine learning algorithms by fine-tuning a T5 model, demonstrating expertise in adapting models for specialized datasets and improving data interpretation.}}

            \resumeItem{\normalsize{Orchestrated workflow with LangChain/FastAPI and a FAISS vector database, achieving a 90\% latency reduction for real-time semantic search, crucial for time-sensitive data processing.}}

          \resumeItemListEnd
          \vspace{-13pt}

     \resumeProjectHeading
          {\href{https://github.com/losthumanity/market-sentiment}{\textbf{\large{\underline{Data Ingestion Pipeline for Market Sentiment Analysis}}} \faExternalLink} $|$ \large{\underline{AWS, Python, MySQL, Docker}}}{}\\
          \resumeItemListStart

            \resumeItem{\normalsize{Architected a real-time, event-driven data pipeline on AWS using Python to process data from 20+ sources, ensuring data integrity for critical systems.}}

            \resumeItem{\normalsize{Implemented optimized queries and aggregations, reducing data retrieval latency by 60\% for real-time dashboards, essential for responsive system performance.}}

            \resumeItem{\normalsize{Automated deployment with a Dockerized CI/CD pipeline leveraging AWS Lambda, demonstrating strong software engineering best practices and efficiency for mission-critical systems.}}

          \resumeItemListEnd
          \vspace{-13pt}

    \resumeSubHeadingListEnd
\vspace{-5pt}

%-----------TECHNICAL SKILLS-----------
\section{TECHNICAL SKILLS}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{\normalsize{Languages:}}{  \normalsize{Python, Java, SQL, Bash}} \\
     \textbf{\normalsize{AI/ML Frameworks:}}{  \normalsize{PyTorch, Pandas, NumPy, LangChain, LlamaIndex}} \\
     \textbf{\normalsize{Backend/Cloud: }}{  \normalsize{Docker, AWS Lambda, FastAPI, Microservices, Spring Boot}} \\
     \textbf{\normalsize{Core Concepts:}}{  \normalsize{Algorithms, Data Structures, Object-Oriented Programming (OOP)}} \\
     \textbf{\normalsize{Databases:}}{  \normalsize{Vector Databases (ChromaDB, FAISS), MySQL, MongoDB}} \\
     \textbf{\normalsize{Developer Tools:}}
    {\normalsize{Git, GitHub, CI/CD, Jupyter, Postman}} \\

    }}
 \end{itemize}
 \vspace{-15pt}

%-----------CERTIFICATIONS---------------
\section{CERTIFICATIONS}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{\normalsize{Generative AI with Large Language Models }}{\normalsize{by DeepLearning.ai}} \\
     \textbf{\normalsize{Deep Learning Specialization}}{ \normalsize{by DeepLearning.AI}}\\
     \textbf{\normalsize{Fundamentals of Deep Learning}}{ \normalsize{by Nvidia}}\\
    }}
 \end{itemize}
 \vspace{-11pt}

\section{EXTRACURRICULAR}
    \resumeSubHeadingListStart
        \resumeItemListStart
            \resumeItem{\normalsize{\textbf{IEEE Research Publication:} Authored a paper, \textit{"Securing Automobiles using Iris Recognition,"} accepted for presentation at the \textbf{IEEE ESCI-2025} conference; distilled complex CNN concepts into practitioner-focused slides.}}
            \resumeItem{\normalsize{Secured a \textbf{Top 10 finish (Top 7\%)} among 150 teams at Smart India Hackathon 2024 by architecting an AI-powered Drug Inventory and Supply Chain Tracking system; led scope definition workshops and prioritized user stories.}}
            \resumeItem{\normalsize{\textbf{CSI Workshop Lead:} Led 3 technical workshops on Python \& Data Structures, mentoring 50+ junior students; designed structured curricula and feedback loops to improve learning outcomes.}}
        \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-11pt}

\end{document}